%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\footskip}{4.08003pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.0cm, top=1cm, right=1cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\footskip}{4.08003pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Ting-Wei Chou} % Your Name
\newcommand{\phone}{966523230}
\newcommand{\emaila}{userwei.cs12@nycu.edu.tw}



\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------


\parbox{\dimexpr\linewidth-0.3cm\relax}{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} \\ 
  {\raisebox{0.0\height}{\footnotesize \faPhone}\ +886-\phone} & \href{https://github.com/chou-ting-wei}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {chou-ting-wei}}\\
  \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize 
 \faEnvelope}\ {\emaila}}&\href{https://www.linkedin.com/in/userwei}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {Ting-Wei Chou}}
\end{tabularx}
}





%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Yang Ming Chiao Tung University}{GPA: 4.25, Ranking: 2/192}
      {Bachelor of Science in Computer Science}{2023 - 2027 (Expected)}
  \resumeSubHeadingListEnd
\vspace{-5.5mm}
%



% -----------EXPERIENCE-----------------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.linkedin.com/company/nycu-csit/}{NYCU CS Information Technology Center}}{}
      {Net Team Member, Teaching Assistant}{July 2024 - Present}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Managed laboratory networks, designed and set up data center networks, and prepared CCNA course content.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-8.5mm}



%-----------PROJECTS-----------------
\section{\textbf{Projects}}
\resumeSubHeadingListStart

    \resumeProject
      {\href{https://github.com/chou-ting-wei/NYCU_Service-Learning-Nanao}{Pain Interaction System}} %Project Name
      {A platform for effectively managing and recording pain data} %Project Name, Location Name
      {June 2024} %Event Dates

      \resumeItemListStart
        \item {Developed a full-stack web application using React and Vite for the frontend, and NestJS for the backend.}
        \item {Managed the application's database with MySQL, ensuring reliable data storage and retrieval.}
        \item {Implemented containerized deployment using Docker for consistent environments across development and production.}
        \item {Tools \& technologies used: Docker, React, NestJS, MySQL.}
    \resumeItemListEnd
    \vspace{-2.0mm}

    \resumeProject
      {\href{https://github.com/chou-ting-wei/NYCU_DBMS-Final-Project}{NBA Stat}} %Project Name
      {A database-driven web platform for NBA player and team statistics} %Project Name, Location Name
      {April 2024} %Event Dates

      \resumeItemListStart
        \item Designed and developed using PHP for backend logic and Bootstrap for a responsive frontend interface.
        \item Implemented database queries with MySQL to efficiently handle and display large datasets of player and team statistics.
        \item Developed interactive features, including player/team search, a voting system, and a discussion forum.
        \item {Tools \& technologies used: Bootstrap, MySQL, JavaScript, PHP.}
      \resumeItemListEnd
    \vspace{-2.0mm}
      
    \resumeProject
      {\href{https://github.com/chou-ting-wei/NYCU_OOP-Dungeon}{Dungeon}} %Project Name
      {A text-based RPG game developed using C++ and object-oriented programming} %Project Name, Location Name
      {April 2024} %Event Dates

      \resumeItemListStart
        \item Designed and implemented a dungeon exploration system where players battle monsters and find exits to escape.
        \item Utilized C++ object-oriented programming principles, including inheritance, polymorphism, and encapsulation.
        \item Developed and the game using CMake and Makefile for cross-platform compatibility.
        \item Tools \& technologies used: C++, CMake, Makefile.
      \resumeItemListEnd
    \vspace{-2.0mm}

  \resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------Achievements-----------------
\section{\textbf{Achievements}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumePOR{Academic Achievements Awards } % Award
    {} % Event
    {Spring 2024} %Event Year
\resumePOR{Foundation Academic Course Award } % Award
    {Digital Circuit Design,  Computer Organization} % Event
    {Spring 2024} %Event Year
\resumePOR{Bronze Award } % Award
    {The 2023 ICPC Asia Taoyuan Regional Programming Contest} % Event
    {October 2023} %Event Year
\resumeSubHeadingListEnd
\vspace{-5mm}

%-----------Positions of Responsibility-----------------
\section{\textbf{Extracurricular Activities}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumePOR{Development Team Leader } % Position
    {\href{https://github.com/Official-Meichu-Hackathon}{Meichu Hackathon}} %Club,Event
    {November 2024 - Present} %Tenure Period
\resumePOR{Core Team Member (Technical Team) } % Position
    {\href{https://gdg.community.dev/gdg-on-campus-national-yang-ming-chiao-tung-university-hsinchu-city-taiwan/}{NYCU Google Developer Groups}} %Club,Event
    {September 2024 - Present} %Tenure Period
\resumePOR{Development Team Member } % Position
    {\href{https://github.com/NCTUCSUnion}{NYCU CS Student Association}} %Club,Event
    {June 2024 - Present} %Tenure Period
    
\resumeSubHeadingListEnd
\vspace{-5mm}


%-----------Technical skills-----------------
\section{\textbf{Technical Skills}}
\resumeSubHeadingListStart
\resumeProject
  {Programming Languages}
  {C, C++, Java, JavaScript, PHP, Python, Shell Scripts, SQL, Verilog}
  {}

\resumeProject
  {Frameworks}
  {Bootstrap, Flask, Next.js, Tailwind CSS, Vue}
  {} 

\resumeProject
  {Tools}
  {Docker, Git, Hugo, LaTeX, Makefile, Markdown, React}
  {} 

\resumeSubHeadingListEnd
\vspace{-16pt}


%-------------------------------------------
\end{document}
